Autonomous Realization of Simple Machines

### 2014-05-26 doc/paper/paper.tex
did the references. still need to finish results

A challenge in long-term manipulation tasks is the accumulation of error over the course of the
executions. To remedy such an error build-up, at the current state of our work, the authors
intervene and instruct the robot to minimize its error if necessary. One of the main causes of this
inaccuracy is the reliability of the RGBD data. We observe that a mean error of 2-3 cm within a 1 m
bound increases up to 10 cm with 4 meters. The proportional increase in error with respect to
distance suggest a camera calibration problem which can be addressed with bundle adjustment \cite{dasgupta1999making}.

@@

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.9\linewidth]{Figures/controller.png}
  \caption{The mechanical advantage in forces}
  \label{fig:controller}
\end{figure}

\subsection{}

\newpage
\bibliographystyle{plain}
\bibliography{references}

>>>>

A challenge in long-term manipulation tasks is the accumulation of error over the course of the
executions. To remedy such an error build-up, at the current state of our work, the authors
intervene and instruct the robot to minimize its error if necessary. One of the main causes of this
inaccuracy is the reliability of the RGBD data. We observe that a mean error of 2-3 cm within a 1 m
bound increases up to 10 cm with 4 meters. The proportional increase in error with respect to
distance suggest a camera calibration problem which can be addressed with bundle adjustment \cite{pradeep2014calibrating}.

@@

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.9\linewidth]{Figures/controller.png}
  \caption{The oscillations and steady state error in following a reference velocity profile.}
  \label{fig:controller}
\end{figure}

\subsubsection{Manipulation of Heavy Objects}

We offer two insights from our experiments. First, the manipulation of heavy objects brings about
interesting challenges. If the object inertia model is not known, the system can be thrown off
balance easily. Moreover, when the mass of the object is mostly on one of the wheels, the robot can
start spinning since one wheel has to accommodate the extra weight.

\newpage
% \bibliographystyle{unsrt}
% \bibliography{references}

\begin{thebibliography}{27}

\bibitem{erdogan2013planning} Erdogan, C., Stilman, M: Planning in constraint space: Automated design of
functional structures. ICRA, 2013.
\bibitem{erdogan2014incorporating} Erdogan, C., Stilman, M: Incorporating kinodynamic constraints in automated
design of simple machines. IROS, 2014.
\bibitem{vidal2006branching} Vincent, V., Geffner, H.: Branching and pruning: An optimal temporal pocl planner
based on constraint programming. AI, 2006.
\bibitem{yu2011make} Yu, L. F., Yeung, S. K., Tang, C. K., Terzopoulos, D., Chan, T. F., Osher, S: Make it home:
automatic optim. of furniture arrangement. In Siggraph, 2011.
\bibitem{beetz2010cram} Beetz, M., Mosenlechner, L., Tenorth, M: Crama cognitive robot
abstract machine for everyday manipulation in human environments. In IROS,
2010.
\bibitem{stilman2005navigation} Stilman, M., Kuffner, J. J.: Navigation among movable obstacles: Real-
time reasoning in complex environments. IJHR, 2005.
\bibitem{kemp2007challenges} Kemp, C. C., Edsinger, A., Torres-Jara, E: Challenges for robot
manipulation in human environments. IEEE Robotics and Automation Magazine,
14(1):20, 2007.
\bibitem{kuindersma2009dexterous} Kuindersma, S. R., Hannigan, E., Ruiken, D., and Grupen, R. A:
Dexterous mobility with the ubot-5 mobile manipulator. ICAR, 2009.
\bibitem{srinivasa2010herb}  Srinivasa, S. S., Ferguson, D., Helfrich, C. J., Berenson, D., 
Collet, A., Diankov, R., Gallagher, R., Hollinger, G., Kuffner, J., and
Weghe, M. V.. Herb: a home exploring robotic butler. Autonomous Robots,
28(1):5–20, 2010.
\bibitem{nishiwaki2000design} Nishiwaki, K., Sugihara, T., Kagami, S., Kanehiro, F.,
Inaba, M., and Inoue, H.: Design and development of research platform for perception-action 
integration in humanoid robot: H6. IROS, 2000.
\bibitem{dasgupta1999making} Dasgupta, A., Nakamura, Y.: Making feasible walking motion of
humanoid robots from human motion capture data. ICRA, 1999.
\bibitem{yamauchi2004packbot} Yamauchi, M. B.: Packbot: a versatile platform for military robotics. In Defense
and Security, pages 228–237. International Society for Optics and Photonics, 2004.
\bibitem{saranli2001rhex} Saranli, U., Buehler, M., Koditschek, D. E.. Rhex: A simple and
highly mobile hexapod robot. IJRR, 2001.
\bibitem{newell1961gps} Newell, A., Simon, H.: GPS, a program that simulates human thought.
DTIC, '61.
\bibitem{mccarthy1963programs} McCarthy, J.: Programs with common sense. DTIC, 1963.
\bibitem{fulkerson1961network} Fulkerson, D. R.: A network flow computation for project cost curves. Management science, 7(2):167–178, 1961.
\bibitem{taha1975integer} Taha, H.A.: Integer programming: theory, applications, and computations,
volume 975. Academic Press New York, 1975.
\bibitem{fikes1972strips} Fikes, R. E., Nilsson, N. J.: Strips: A new approach to the application of
theorem proving to problem solving. Artificial intelligence, 2(3):189–208, 1972.
\bibitem{stilman2010golem} Stilman, M., Olson, J., Gloss, W.: Golem krang: Dynamically stable
humanoid robot for mobile manipulation. ICRA, 2010.
\bibitem{kuffner2000rrt} Kuffner J.J., LaValle, S.M.: RRT-connect: An efficient approach to single-
query path planning. In ICRA. IEEE, 2000.
\bibitem{tolani2000real} Tolani, D., Goswami, A., Badler, N. I.: Real-time inverse kinematics techniques for anthropomorphic limbs. Graphical models, 62(5):353–388,
2000.
\bibitem{whitney1969resolved} Whitney, D. E.: Resolved motion rate control of manipulators and human pros-
theses. IEEE Transactions on man-machine systems, 1969.
\bibitem{bejczy1977effect} Bejczy, A.K.: Effect of hand-based sensors on manipulator control performance.
Mechanism and Machine Theory, 12(5):547–567, 1977.
\bibitem{goldman1996expressive} Goldman, R., Boddy, M.: Expressive planning and explicit knowledge. AIPS, 1996.
\bibitem{mason1986mechanics} Mason, M.T.: Mechanics and planning of manipulator pushing operations.
The International Journal of Robotics Research, 5(3):53–71, 1986.
\bibitem{pradeep2014calibrating} Pradeep, V., Konolige, K., Berger, E.: Calibrating a multi-arm multi-
sensor robot: A bundle adjustment approach. In Experimental Robotics, 1999.
\bibitem{ha1996trajectory} Ha, Y., Yuta, S.: Trajectory tracking control for navigation of the
inverse pendulum type self-contained mobile robot. Robotics and autonomous systems, 1996.

\end{thebibliography}
